Meesters TODO List

### 2023-04-15 files/Chapter2/generalvibrationmodel.tex

\section{Modal analysis}\label{sec:existence:ModalAnalysis}
\subsection{Timoshenko beam}
To understand what is meant by modal analysis, it is in the first place necessary to consider modes of vibration. And to understand how modal analysis is applied, a Timoshenko beam is used as an example. Specifically, Problem T-1 as it is easy to illustrate the idea of modal analysis.

@@

Therefore $\displaystyle \frac{T''(t)}{T(t)}$ must be a constant. Suppose $\displaystyle \frac{T''(t)}{T(t)} = -\lambda$. Then the function $T$ satisfies the following differential equation
\begin{eqnarray}
	\ddot{T} + \lambda T = 0. \label{eq:1D_Model:ModalAnalysisT}
\end{eqnarray}

If such a $\lambda$ exists, it leads to the following problem called an eigenvalue problem.
\subsubsection*{Problem T-1E}\label{sssec:1D_Model:Problem:T1E}
Find $\lambda \in \mathbb{R}$ and functions $\tilde{w}$ and $\tilde{\phi}$ such that
\begin{eqnarray*}
	-\tilde{w}'' + \tilde{\phi}' &=& \lambda \tilde{w}, \label{eq:1D_Model:ProblemT1E1}\\
	-\alpha \tilde{w}' + \alpha\tilde{\phi} - \frac{1}{\gamma}\tilde{\phi}'' &=& \lambda \tilde{\phi}. \label{eq:1D_Model:ProblemT1E2}
\end{eqnarray*} with boundary conditions $\tilde{w}(0) = \tilde{w}(1) = 0$ and $\tilde{\phi}'(0) = \tilde{\phi}'(1) = 0$.

@@

Combining the solutions of the eigenvalue problem with the solution \eqref{eq:1D_Model:ModalAnalysisTn} yields:
\begin{eqnarray*}
	w_n(x,t) & = & T_n(t)\tilde{w}_n(t), \\
	\phi_n(x,t) & = & T_n(t)\tilde{\phi}_n(x).
\end{eqnarray*} 
Substitution show that these solutions does indeed satisfy the differential equations with the boundary conditions. These solutions are the modal solutions and they are clearly periodic with natural angular frequencies $\sqrt{\lambda_n}$ (consequently the natural frequencies are $\frac{\sqrt{\lambda_n}}{2 \pi})$.

>>>>

\section{Modal analysis}\label{sec:existence:ModalAnalysis}
\subsection{Timoshenko beam}\label{subsec:Timoshenko_Modal_Analsis}
To understand what is meant by modal analysis, it is in the first place necessary to consider modes of vibration. And to understand how modal analysis is applied, a Timoshenko beam is used as an example. Specifically, Problem T-1 as it is easy to illustrate the idea of modal analysis.

@@

Therefore $\displaystyle \frac{T''(t)}{T(t)}$ is a constant. Suppose $\displaystyle \frac{T''(t)}{T(t)} = -\lambda$. This can also be written as the following differential equation
\begin{eqnarray}
	\ddot{T} + \lambda T = 0. \label{eq:1D_Model:ModalAnalysisT}
\end{eqnarray}

To determine if such a number $\lambda$ exists, consider the following eigenvalue problem.
\subsubsection*{Problem T-1E}\label{sssec:1D_Model:Problem:T1E}
Find $\lambda \in \mathbb{R}$ and functions $\tilde{w}$ and $\tilde{\phi}$ such that
\begin{eqnarray*}
	-\tilde{w}'' + \tilde{\phi}' &=& \lambda \tilde{w}, \label{eq:1D_Model:ProblemT1E1}\\
	-\alpha \tilde{w}' + \alpha\tilde{\phi} - \frac{1}{\gamma}\tilde{\phi}'' &=& \lambda \tilde{\phi}. \label{eq:1D_Model:ProblemT1E2}
\end{eqnarray*} with boundary conditions $\tilde{w}(0) = \tilde{w}(1) = 0$ and $\tilde{\phi}'(0) = \tilde{\phi}'(1) = 0$.

@@

Combining the solutions of the eigenvalue problem with the solution \eqref{eq:1D_Model:ModalAnalysisTn} yields:
\begin{eqnarray*}
	w_n(x,t) & = & T_n(t)\tilde{w}_n(t), \\
	\phi_n(x,t) & = & T_n(t)\tilde{\phi}_n(x).
\end{eqnarray*} 
Substitution show that these solutions does indeed satisfy the differential equations \ref{eq:1D_Model:ModalPDE1} and \ref{eq:1D_Model:ModalPDE2} with the boundary conditions. These solutions are the modal solutions and they are clearly periodic with natural angular frequencies $\sqrt{\lambda_n}$ (consequently the natural frequencies are $\frac{\sqrt{\lambda_n}}{2 \pi})$.

### 2023-04-15 files/Chapter4/ModalAnalysisTimo.tex

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Introduction}
An example of modal analysis on a Timoshenko beam is given in section \ref{sec:existence:ModalAnalysis}. In this section, more general theory for modal analysis of te Timoshenko beam theory is discuss, as well as some more examples of the application of the theory.
\section{Eigenvalue problem}\label{sec:Timo:EigenvalueProblem}
In section \ref{ssec:1D_Model:Modal} the idea of modal analysis is explored using a Timoshenko beam as an example. In this section, we look at the work of the authors of [VV06]. The authors gives a method to calculate the eigenvalues and eigenfunctions for the Timoshenko beam theory.

Consider a general eigenvalue problem for the Timoshenko beam theory.

\sout{The next step is to find a method to {easily} calculate the eigenvalues and eigenvectors for the Timoshenko beam models {theory}}.

\sout{For this section, the work of the authors of [VV06] is discussed. {Consider the article [VV06].} In this article the authors present a method to calculate the exact eigenvalues and eigenvectors for the Timoshenko beam theory}.

\sout{To discuss the work of [VV06], a general eigenvalue problem is required. So consider only the differential equations of an eigenvalue problem for a Timoshenko beam. The reader can refer to Problem T-1E in section \ref{ssec:1D_Model:Modal} for a more specific example of the derivation of the eigenvalue problems for the Timoshenko beam theory.}

\sout{In section \ref{ssec:1D_Model:Modal}, the eigenvalue for Problem T-1 is given as Problem T-1E. }
\textcolor{red}{Probleem se naam verander vanaf Differential equations for the eigenvalue problem}
\subsubsection{General eigenvalue problem} \label{sssec:Timo:EigenvalueProblem}
Find functions $u$ and $\phi$ and a real number $\lambda$ satisfying the following equations
\begin{eqnarray}
-u'' + \phi' &=& \lambda u, \label{eq:Timo:EigenvalueProblem1}\\
-\alpha u' + \alpha\phi - \frac{1}{\gamma}\phi'' &=& \lambda\phi.\label{eq:Timo:EigenvalueProblem2}
\end{eqnarray}

@@

The authors of [VV06] first derive a general solution for the system of ordinary differential equations \eqref{eq:Timo:EigenvalueProblem1} and \eqref{eq:Timo:EigenvalueProblem2}. In [VV06] the authors show that for the Timoshenko models in this dissertation $\lambda$ non-negative. Assume that the solution is of the form $\langle u, \phi \rangle = e^{mx}\bar{w}$ where $m\in \mathbb{R}$ or $m\in \mathbb{C}$. Substitution into \eqref{eq:Timo:EigenvalueProblem1} and \eqref{eq:Timo:EigenvalueProblem2} yields:
\begin{eqnarray*}
-m^{2}e^{mx}w_{1}+me^{mx}w_{2}&=&\lambda e^{mx}w_{1},\\
-\frac{1}{\gamma}m^{2}e^{mx}w_{2}-\alpha me^{mx}w_{1}+\alpha e^{mx}w_{2}&=&\lambda e^{mx}w_{2}.
\end{eqnarray*}

@@

Now if $m^{2} \neq 0$, we consider the system $A\bar{w}=0$ with $w_{1} = m$ and $w_{2} = m^{2} + \lambda$. From [VV06], the parameters $\omega$, $\mu$ and $\theta$ are uniquely determined by $\lambda$.
\begin{eqnarray}
	\omega^2 & = & \frac{1}{2}\lambda(1+\gamma)(\Delta^{\frac{1}{2}}+1) \ \textrm{ for } \lambda >0\\
	\mu^2 & = & \frac{1}{2}\lambda(1+\gamma)(\Delta^{\frac{1}{2}}-1) \ \textrm{ for } \lambda < \alpha\\
	\theta^2 & = & \frac{1}{2}\lambda(1+\gamma)(1-\Delta^{\frac{1}{2}}) \ \textrm{ for } \lambda > \alpha
\end{eqnarray}

 The three cases $\lambda < \alpha$, $\lambda = \alpha$ and $\lambda > \alpha$ are considered separately by the authors of [VV06]. The general solution from [VV06] for each case is presented below.

@@

The next step is to determine the solution of the general eigenvalue problem. The strategy to obtain the eigenvalues and eigenvectors are described in detail in [VV06] using an example. A summary of the strategy is presented here.\\

@@

The following two sections provide examples of this strategy applied to beam models. These examples are also in [VV06].

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Introduction}
An example of modal analysis on a Timoshenko beam is given in section \ref{sec:existence:ModalAnalysis}. In this section, more general theory for modal analysis of te Timoshenko beam theory is discuss, as well as some more examples of the application of the theory.
\section{Eigenvalue problem}\label{sec:Timo:EigenvalueProblem}
This section is a discussion of a systematic method to solve the eigenvalue problem for the Timoshenko beam theory. The article discussed is \cite{VV06}.

Consider a general eigenvalue problem for a Timoshenko beam Problem.
\subsubsection{General eigenvalue problem} \label{sssec:Timo:EigenvalueProblem}
Find functions $u$ and $\phi$ and a real number $\lambda$ satisfying the following equations
\begin{eqnarray}
-u'' + \phi' &=& \lambda u, \label{eq:Timo:EigenvalueProblem1}\\
-\alpha u' + \alpha\phi - \frac{1}{\gamma}\phi'' &=& \lambda\phi.\label{eq:Timo:EigenvalueProblem2}
\end{eqnarray}

@@

The authors of \cite{VV06} first derive a general solution for the system of ordinary differential equations \eqref{eq:Timo:EigenvalueProblem1} and \eqref{eq:Timo:EigenvalueProblem2}. In \cite{VV06} the authors show that for the Timoshenko models in this dissertation $\lambda$ non-negative. Assume that the solution is of the form $\langle u, \phi \rangle = e^{mx}\bar{w}$ where $m\in \mathbb{R}$ or $m\in \mathbb{C}$. Substitution into \eqref{eq:Timo:EigenvalueProblem1} and \eqref{eq:Timo:EigenvalueProblem2} yields:
\begin{eqnarray*}
-m^{2}e^{mx}w_{1}+me^{mx}w_{2}&=&\lambda e^{mx}w_{1},\\
-\frac{1}{\gamma}m^{2}e^{mx}w_{2}-\alpha me^{mx}w_{1}+\alpha e^{mx}w_{2}&=&\lambda e^{mx}w_{2}.
\end{eqnarray*}

@@

Now if $m^{2} \neq 0$, we consider the system $A\bar{w}=0$ with $w_{1} = m$ and $w_{2} = m^{2} + \lambda$. From \cite{VV06}, the parameters $\omega$, $\mu$ and $\theta$ are uniquely determined by $\lambda$.
\begin{eqnarray}
	\omega^2 & = & \frac{1}{2}\lambda(1+\gamma)(\Delta^{\frac{1}{2}}+1) \ \textrm{ for } \lambda >0\\
	\mu^2 & = & \frac{1}{2}\lambda(1+\gamma)(\Delta^{\frac{1}{2}}-1) \ \textrm{ for } \lambda < \alpha\\
	\theta^2 & = & \frac{1}{2}\lambda(1+\gamma)(1-\Delta^{\frac{1}{2}}) \ \textrm{ for } \lambda > \alpha
\end{eqnarray}

 The three cases $\lambda < \alpha$, $\lambda = \alpha$ and $\lambda > \alpha$ are considered separately by the authors of \cite{VV06}. The general solution from \cite{VV06} for each case is presented below.

@@

The next step is to determine the solution of the general eigenvalue problem. The strategy to obtain the eigenvalues and eigenvectors are described in detail in \cite{VV06} using an example. A summary of the strategy is presented here.\\

@@

In \cite{VV06}, the steps are explained using the example of a pinned-pinned beam, the same model as in section \ref{subsec:Timoshenko_Modal_Analsis}. For $\lambda < \alpha$ the general solution reduces to $\langle u , \phi \rangle = \langle \sin, \cos \rangle$. For $\lambda > \alpha$, the general solution also reduces to $\langle u , \phi \rangle = \langle \sin, \cos \rangle$. For $\lambda = \alpha$, the general solution reduces to $\langle u , \phi \rangle = \langle 0, 1 \rangle$.\\

This is proved rigourously in \cite{VV06} and also proved Theorem 1 in section \ref{subsec:Timoshenko_Modal_Analsis}.

The following two sections provide examples of this strategy applied to beam models. These examples are also in \cite{VV06}.
